Exact asymptotic expressions for local clustering in hyperbolic random graphs \\ \TM{ I prefer not to use the term ``hyperbolic random graph". Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}

### 2019-01-19 concentration.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

\noindent {\bf Case $\bm{k_n = \bigT{1}}$:}\\
This proof is very similar to the previous one. Here however, we write
\begin{align*}
	\rho_{n}(p,p^\prime,k_n,k_n) &= \Prob{X_1(p,p^\prime) + X_3(p,p^\prime) = k_n, X_2(p,p^\prime) + X_3(p,p^\prime) = k_n}\\
	&= \Prob{X_3(p,p^\prime) = 0}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} 
		+ \bigO{\Prob{X_3(p,p^\prime) \ge 1}}.
\end{align*}
By definition of $\mathcal{E}(k_n)$ and the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:common_neighbors_Pcal_n} we get that for $(p,p^\prime) \in \mathcal{E}(k_n)$
\[
	\Exp{X_3(p,p^\prime)} \le \bigT{1} \log(n)^{-(2\alpha - 1)} + \bigT{1}e^{-(\alpha - \frac{1}{2})R_n},
\]
where we used that in this case $\Mu{\BallPon{p}}, \Mu{\BallPon{p^\prime}} = \bigT{1}$ and $|x-x^\prime| \le \bigT{1} e^{R_n/2}$. This implies that
\[
	\Prob{X_3(p,p^\prime) \ge 1} \le \Exp{X_{3}(p,p^\prime)} = \bigO{\log(n)^{-(2\alpha - 1)}},
\] 
Next we observe that by definition of $\mathcal{E}(k_n)$ the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:disjoint_neighbors_P_n_large} satisfies
\[
	\sup_{(p,p^\prime) \in \mathcal{E}(k_n)} \phi_n(p,p^\prime) = \bigO{\log(n)^{-(2\alpha - 1)}}.
\]
Therefore we can apply the exact same arguments as for the case $k_n \to \infty$ to obtain
\begin{align*}
	&\int_{\mathcal{E}(k_n)} \rho_n(y,y^\prime,k_n,k_N) h(y)h(y^\prime) 
		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
	&=(1+\smallO{1})\int_{\mathcal{E}(k_n)} \hspace{-5pt}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} h(y) h(y^\prime) 	
		f_{\alpha,\nu}(x,y)f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
	&\hspace{10pt}+ \bigO{1}\log(n)^{-(2\alpha - 1)} \int_{\mathcal{E}(k_n)}
		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
	&= (1+\smallO{1})\int_{\mathcal{E}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,
\end{align*}
where we used that
\[
	\log(n)^{-(2\alpha - 1)}\int_{\mathcal{E}(k_n)}
			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime
\]
is of smaller order than
\[
	\int_{\mathcal{E}_(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
\]
\end{proof}

@@

The prove is split over the two cases $k_n = \bigT{1}$ and $k_n \to \infty$.

\subsubsection*{The case $\bm{k_n = \bigT{1}}$}

Take $a_n = 2\log\left((k_n + C\log(n))/\xi_{\alpha, \nu}\right)$ and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $(p,p^\prime) \in \mathcal{E}(k_n)$ as defined in~\eqref{eq:def_joint_degree_set_E_constant_k}. We will show that the expected difference between $I_{a,b}$ and $I_{a,b}^\ast$ is of smaller order than $\Exp{T_\Pcal(k_n)}^2$ so that we only need to consider $I_{a,b}^\ast$.

Since 
\[
	|x - x^\prime| \le \left(e^{y/2} + e^{y^\prime/2}\right)\left(\frac{k_n + C \log(n)}{\xi_{\alpha,\nu}}\right)
	= \bigO{\log(n)^2}
\] 
for all $p,p ^\prime \in \mathcal{E}_C(k_n)^c$, it follows that
\begin{align*}
	&\Exp{\left|I_{a,b} - I^\ast_{a,b}\right|} \\
	&\le \int_{\mathcal{E}_{C}(k_n)^c} 
		\Exp{\ind{D_{\Pcal,n}(p) = k_n - i, \, D_{\Pcal,n}(p^\prime) = k_n - i^\prime} J_b(p,p^\prime)}
		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{J_b(p,p^\prime)}
		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)}
		\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} 
		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
	&\le \bigO{\log(n)^2} \left(\int_{\Kcal_{C}(k_n)} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)} 
		f_{\alpha, \nu}(x,y) \dd x \dd y\right)	
		\left(\int_0^{a_n} \Delta_\Pcal(y^\prime) e^{-\alpha y^\prime} \dd y^\prime\right) \\
	&= \bigO{\log(n)^2 s_\alpha(k_n) \Exp{T_\Pcal(k_n)}},
\end{align*}
where the last line follows from Corollary~\ref{cor:adjusted_triangle_counting_P_n} and Proposition~\ref{prop:asymptotics_Delta_y_P} which states that for all $0 < y^\prime \le a_n$, $\Delta_\Pcal(y^\prime) = \bigO{s_\alpha(k_n)}$. Next we note that $\Exp{T_\Pcal(k_n)} = \bigT{n k_n^{-(2\alpha - 1)} s_\alpha(k_n)}$, hence $\log(n)^2 s_\alpha(k_n) = \smallO{\Exp{T_\Pcal(k_n)}}$ and therefore we conclude that
\[
	\Exp{\left|I_{a,b} - I^\ast_{a,b}\right|} = \smallO{\Exp{T_\Pcal(k_n)}^2}.
\]

We now proceed with computing $I_{a,b}^\ast$. For this we note that the parts of the neighborhoods $\BallPon{p}$ and $\BallPon{p^\prime}$ where $y_1, y_1^\prime \le h(p,p^\prime)$ are disjoint, see Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3}. In particular, this implies that when $b \ne 0$ this can only be if one of the $y_1, y_2, y_1^\prime, y_2^\prime$ exceeds $h(p,p^\prime)$. Now we observe that for $(p,p^\prime) \in \mathcal{E}(k_n)$ we have
\begin{align*}
	\int_{h(p,p^\prime)}^{R_n}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
	&= \bigO{e^{y/2} e^{-(\alpha - \frac{1}{2})h(p,p^\prime)}}
		= \bigO{\log(n)^{-(2\alpha - 1)}},
\end{align*}
while
\begin{align*}
	\int_0^{h(p,p^\prime)}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
	&= \bigO{1}.
\end{align*} 
Hence if $b \ne 0$ then it follows that $\Exp{J_b} = \bigO{\log(n)^{-(2\alpha - 1)}}$ and we conclude that 
\[
	\Exp{I_{a,b}} = \bigO{n^2 \log(n)^{-(2\alpha - 1)}} = \smallO{\Exp{T_\Pcal(k_n)}^2}
\]

For $I_{0,0}^\ast$ we define
\[
	\mathcal{J}_1^\ast = \int_{\Rcal_n^2} \ind{0\le y_1, y_2 \le h(p,p^\prime)} \widetilde{T}_{\Pcal,n}(p,p_1,p_2) 
			f_{\alpha,\nu}(x_1,y_1)	f_{\alpha,\nu}(x_2,y_2) \dd x_2 \dd x_1 \dd y_2 \dd y_1
\] 
and define $\mathcal{J}_2^\ast$ in a similar way by interchanging the primed and non-primed variables. Then we get
\[
	\Exp{J_0(p,p^\prime)} = \mathcal{J}_1^\ast \mathcal{J}_2^\ast + \bigO{\log(n)^{-(2\alpha - 1)}}.
\]
In addition, for $(p,p^\prime) \in \mathcal{E}(k_n)$ Corollary~\ref{cor:adjusted_triangle_counting_P_n} implies that 
\[
	\mathcal{J}_1^\ast = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal,n}(p)} = (1 + \smallO{1})\binom{k_n}{2} \Delta_\Pcal(y),
\] 
and similar for $\mathcal{J}_2^\ast$, while Lemma~\ref{lem:joint_degree_factorization} states that
\begin{align*}
	&\hspace{-30pt}\int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
	&= (1+\smallO{1})\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha,\nu}(x,y) \dd x \dd y\right)^2.
\end{align*}
We therefore conclude that
\begin{align*}
	\Exp{I_{0,0}^\ast} 
	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Exp{J_0(p,p^\prime)}
		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y \\
	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
	&\hspace{10pt}+ \bigO{\log(n)^{-(2\alpha - 1)}n^2} \\
	&= (1 + \smallO{1}) \binom{k_n}{2}^2 
		\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha,\nu}(x,y) \dd x \dd y\right)^2 \\
	&= (1 + \smallO{1})\Exp{T_\Pcal(k_n)}^2,
\end{align*}
which finishes the proof for $k_n = \bigT{1}$

\subsubsection*{The case $\bm{k_n \to \infty}$}

Recall the definition of $\mathcal{E}_\varepsilon(k_n)$
\[
	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Kcal_C(k_n) \times \Kcal_C(k_n) 
	\, : \, \Exp{\left|\Ncal_{\Pcal,n}^c(p,p^\prime)\right|} \ge k_n^{\varepsilon} \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}
\]
let $\mathcal{E}_\varepsilon(k_n)^c$ denote its complement and, similar to the previous case, let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $p,p^\prime \in \Pcal_n \cap \mathcal{E}_\varepsilon(k_n)$. We first show that
\begin{equation}\label{eq:I_ab_ast_main}
	\Exp{I_{a,b} - I_{a,b}^\ast} = \smallO{\Exp{T_{\Pcal,n}(k_n)}^2},
\end{equation}
so that for the remainder of the proof we only need to consider $p, p^\prime \in \mathcal{E}_\varepsilon(k_n)$ and hence, we can apply Lemma \ref{lem:joint_degree_factorization}. For this we note that by Lemma \ref{lem:disjoint_neighbors_P_n} and Lemma \ref{lem:disjoint_neighbors_P_n_large} we have for $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ that $\Exp{\left|\Ncal_{\Pcal,n}(p\Delta p^\prime)\right|} \le k_n^{\varepsilon}$ implies that eventually and $|x-x^\prime| \le k_n^{1+\varepsilon}$. In particular $|x - x^\prime| \le k_n^{1+\varepsilon}$ for all $(p, p^\prime) \in \mathcal{E}_{\varepsilon}(k_n)^c$. Therefore, we have
\begin{align*}
	&\Exp{I_{a,b} - I_{a,b}^\ast}\\
	&\le \int_{\Kcal_C(k_n)^2 \setminus \mathcal{E}_\varepsilon(k_n)} \rho(p, p^\prime, k - i, k - i^\prime) 
		\Exp{J_b(p,p^\prime)} f_{\alpha,\nu}(x,y) f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
	&\le \int_{\Kcal_C(k_n)^2 \setminus \mathcal{E}_\varepsilon(k_n)} \rho(p, p^\prime, k - i, k - i^\prime) 
		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y) f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
	&= \bigO{\int_{\Kcal_C(k_n)^2} \ind{|x-x^\prime| \le k_n^{1 + \varepsilon}} \rho_{y}(k) 
		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y) f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy}\\
	&= \bigO{k_n^{1+\varepsilon} \binom{k_n}{2} \left(\int_{a_n^-}^{a_n^+} \Delta_{\Pcal}(y^\prime) 
			e^{-\alpha y^\prime} \, dy^\prime\right) \Exp{T_{\Pcal,n}(k_n)}}\\
	&= \bigO{k_n^{3 + \varepsilon -2\alpha} s_\alpha(k_n) \Exp{T_{\Pcal,n}(k_n)}}\\
	&= \smallO{n k_n^{-(2\alpha - 1)}s_\alpha(k_n) \Exp{T_{\Pcal,n}(k_n)}} = \smallO{\Exp{T_{\Pcal,n}(k_n)}^2},
\end{align*}
which proves \eqref{eq:I_ab_ast_main}. Here we used that $k_n^{2 + \varepsilon} = \smallO{n}$ and $\Exp{T_{\Pcal,n}(k_n)} = \bigT{n k_n^{-(2\alpha - 1)}s_\alpha(k_n)}$ for the last line.

>>>>

%\noindent {\bf Case $\bm{k_n = \bigT{1}}$:}\\
%This proof is very similar to the previous one. Here however, we write
%\begin{align*}
%	\rho_{n}(p,p^\prime,k_n,k_n) &= \Prob{X_1(p,p^\prime) + X_3(p,p^\prime) = k_n, X_2(p,p^\prime) + X_3(p,p^\prime) = k_n}\\
%	&= \Prob{X_3(p,p^\prime) = 0}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} 
%		+ \bigO{\Prob{X_3(p,p^\prime) \ge 1}}.
%\end{align*}
%By definition of $\mathcal{E}(k_n)$ and the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:common_neighbors_Pcal_n} we get that for $(p,p^\prime) \in \mathcal{E}(k_n)$
%\[
%	\Exp{X_3(p,p^\prime)} \le \bigT{1} \log(n)^{-(2\alpha - 1)} + \bigT{1}e^{-(\alpha - \frac{1}{2})R_n},
%\]
%where we used that in this case $\Mu{\BallPon{p}}, \Mu{\BallPon{p^\prime}} = \bigT{1}$ and $|x-x^\prime| \le \bigT{1} e^{R_n/2}$. This implies that
%\[
%	\Prob{X_3(p,p^\prime) \ge 1} \le \Exp{X_{3}(p,p^\prime)} = \bigO{\log(n)^{-(2\alpha - 1)}},
%\] 
%Next we observe that by definition of $\mathcal{E}(k_n)$ the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:disjoint_neighbors_P_n_large} satisfies
%\[
%	\sup_{(p,p^\prime) \in \mathcal{E}(k_n)} \phi_n(p,p^\prime) = \bigO{\log(n)^{-(2\alpha - 1)}}.
%\]
%Therefore we can apply the exact same arguments as for the case $k_n \to \infty$ to obtain
%\begin{align*}
%	&\int_{\mathcal{E}(k_n)} \rho_n(y,y^\prime,k_n,k_N) h(y)h(y^\prime) 
%		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
%	&=(1+\smallO{1})\int_{\mathcal{E}(k_n)} \hspace{-5pt}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} h(y) h(y^\prime) 	
%		f_{\alpha,\nu}(x,y)f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
%	&\hspace{10pt}+ \bigO{1}\log(n)^{-(2\alpha - 1)} \int_{\mathcal{E}(k_n)}
%		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
%	&= (1+\smallO{1})\int_{\mathcal{E}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
%		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,
%\end{align*}
%where we used that
%\[
%	\log(n)^{-(2\alpha - 1)}\int_{\mathcal{E}(k_n)}
%			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime
%\]
%is of smaller order than
%\[
%	\int_{\mathcal{E}_(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
%			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
%\]
\end{proof}

@@

%The prove is split over the two cases $k_n = \bigT{1}$ and $k_n \to \infty$. 
%
%\subsubsection*{The case $\bm{k_n = \bigT{1}}$}
%
%Take $a_n = 2\log\left((k_n + C\log(n))/\xi_{\alpha, \nu}\right)$ and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $(p,p^\prime) \in \mathcal{E}(k_n)$ as defined in~\eqref{eq:def_joint_degree_set_E_constant_k}. We will show that the expected difference between $I_{a,b}$ and $I_{a,b}^\ast$ is of smaller order than $\Exp{T_\Pcal(k_n)}^2$ so that we only need to consider $I_{a,b}^\ast$. 
%
%Since 
%\[
%	|x - x^\prime| \le \left(e^{y/2} + e^{y^\prime/2}\right)\left(\frac{k_n + C \log(n)}{\xi_{\alpha,\nu}}\right)
%	= \bigO{\log(n)^2}
%\] 
%for all $p,p ^\prime \in \mathcal{E}_C(k_n)^c$, it follows that
%\begin{align*}
%	&\Exp{\left|I_{a,b} - I^\ast_{a,b}\right|} \\
%	&\le \int_{\mathcal{E}_{C}(k_n)^c} 
%		\Exp{\ind{D_{\Pcal,n}(p) = k_n - i, \, D_{\Pcal,n}(p^\prime) = k_n - i^\prime} J_b(p,p^\prime)}
%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
%	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{J_b(p,p^\prime)}
%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
%	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)}
%		\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} 
%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
%	&\le \bigO{\log(n)^2} \left(\int_{\Kcal_{C}(k_n)} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)} 
%		f_{\alpha, \nu}(x,y) \dd x \dd y\right)	
%		\left(\int_0^{a_n} \Delta_\Pcal(y^\prime) e^{-\alpha y^\prime} \dd y^\prime\right) \\
%	&= \bigO{\log(n)^2 s_\alpha(k_n) \Exp{T_\Pcal(k_n)}},
%\end{align*}
%where the last line follows from Corollary~\ref{cor:adjusted_triangle_counting_P_n} and Proposition~\ref{prop:asymptotics_Delta_y_P} which states that for all $0 < y^\prime \le a_n$, $\Delta_\Pcal(y^\prime) = \bigO{s_\alpha(k_n)}$. Next we note that $\Exp{T_\Pcal(k_n)} = \bigT{n k_n^{-(2\alpha - 1)} s_\alpha(k_n)}$, hence $\log(n)^2 s_\alpha(k_n) = \smallO{\Exp{T_\Pcal(k_n)}}$ and therefore we conclude that
%\[
%	\Exp{\left|I_{a,b} - I^\ast_{a,b}\right|} = \smallO{\Exp{T_\Pcal(k_n)}^2}.
%\]
%
%We now proceed with computing $I_{a,b}^\ast$. For this we note that the parts of the neighborhoods $\BallPon{p}$ and $\BallPon{p^\prime}$ where $y_1, y_1^\prime \le h(p,p^\prime)$ are disjoint, see Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3}. In particular, this implies that when $b \ne 0$ this can only be if one of the $y_1, y_2, y_1^\prime, y_2^\prime$ exceeds $h(p,p^\prime)$. Now we observe that for $(p,p^\prime) \in \mathcal{E}(k_n)$ we have
%\begin{align*}
%	\int_{h(p,p^\prime)}^{R_n}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
%	&= \bigO{e^{y/2} e^{-(\alpha - \frac{1}{2})h(p,p^\prime)}}
%		= \bigO{\log(n)^{-(2\alpha - 1)}},
%\end{align*}
%while
%\begin{align*}
%	\int_0^{h(p,p^\prime)}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
%	&= \bigO{1}.
%\end{align*} 
%Hence if $b \ne 0$ then it follows that $\Exp{J_b} = \bigO{\log(n)^{-(2\alpha - 1)}}$ and we conclude that 
%\[
%	\Exp{I_{a,b}} = \bigO{n^2 \log(n)^{-(2\alpha - 1)}} = \smallO{\Exp{T_\Pcal(k_n)}^2}
%\]
%
%For $I_{0,0}^\ast$ we define
%\[
%	\mathcal{J}_1^\ast = \int_{\Rcal_n^2} \ind{0\le y_1, y_2 \le h(p,p^\prime)} \widetilde{T}_{\Pcal,n}(p,p_1,p_2) 
%			f_{\alpha,\nu}(x_1,y_1)	f_{\alpha,\nu}(x_2,y_2) \dd x_2 \dd x_1 \dd y_2 \dd y_1
%\] 
%and define $\mathcal{J}_2^\ast$ in a similar way by interchanging the primed and non-primed variables. Then we get
%\[
%	\Exp{J_0(p,p^\prime)} = \mathcal{J}_1^\ast \mathcal{J}_2^\ast + \bigO{\log(n)^{-(2\alpha - 1)}}.
%\]
%In addition, for $(p,p^\prime) \in \mathcal{E}(k_n)$ Corollary~\ref{cor:adjusted_triangle_counting_P_n} implies that 
%\[
%	\mathcal{J}_1^\ast = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal,n}(p)} = (1 + \smallO{1})\binom{k_n}{2} \Delta_\Pcal(y),
%\] 
%and similar for $\mathcal{J}_2^\ast$, while Lemma~\ref{lem:joint_degree_factorization} states that
%\begin{align*}
%	&\hspace{-30pt}\int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
%	&= (1+\smallO{1})\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha,\nu}(x,y) \dd x \dd y\right)^2.
%\end{align*}
%We therefore conclude that
%\begin{align*}
%	\Exp{I_{0,0}^\ast} 
%	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Exp{J_0(p,p^\prime)}
%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y \\
%	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
%	&\hspace{10pt}+ \bigO{\log(n)^{-(2\alpha - 1)}n^2} \\
%	&= (1 + \smallO{1}) \binom{k_n}{2}^2 
%		\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha,\nu}(x,y) \dd x \dd y\right)^2 \\
%	&= (1 + \smallO{1})\Exp{T_\Pcal(k_n)}^2,
%\end{align*}
%which finishes the proof for $k_n = \bigT{1}$

Recall the definition of $\mathcal{E}_\varepsilon(k_n)$
\[
	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Kcal_C(k_n) \times \Kcal_C(k_n) 
	\, : \, \Exp{\left|\Ncal_{\Pcal,n}^c(p,p^\prime)\right|} \ge k_n^{\varepsilon} \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}
\]
let $\mathcal{E}_\varepsilon(k_n)^c$ denote its complement and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $p,p^\prime \in \Pcal_n \cap \mathcal{E}_\varepsilon(k_n)$. We first show that
\begin{equation}\label{eq:I_ab_ast_main}
	\Exp{I_{a,b} - I_{a,b}^\ast} = \smallO{\Exp{T_{\Pcal,n}(k_n)}^2},
\end{equation}
so that for the remainder of the proof we only need to consider $p, p^\prime \in \mathcal{E}_\varepsilon(k_n)$ and hence, we can apply Lemma \ref{lem:joint_degree_factorization}. For this we note that by Lemma \ref{lem:disjoint_neighbors_P_n} and Lemma \ref{lem:disjoint_neighbors_P_n_large} we have for $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ that $\Exp{\left|\Ncal_{\Pcal,n}(p\Delta p^\prime)\right|} \le k_n^{\varepsilon}$ implies that eventually and $|x-x^\prime| \le k_n^{1+\varepsilon}$. In particular $|x - x^\prime| \le k_n^{1+\varepsilon}$ for all $(p, p^\prime) \in \mathcal{E}_{\varepsilon}(k_n)^c$. Therefore, we have
\begin{align*}
	&\Exp{I_{a,b} - I_{a,b}^\ast}\\
	&\le \int_{\Kcal_C(k_n)^2 \setminus \mathcal{E}_\varepsilon(k_n)} \rho(p, p^\prime, k - i, k - i^\prime) 
		\Exp{J_b(p,p^\prime)} f_{\alpha,\nu}(x,y) f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
	&\le \int_{\Kcal_C(k_n)^2 \setminus \mathcal{E}_\varepsilon(k_n)} \rho(p, p^\prime, k - i, k - i^\prime) 
		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y) f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
	&= \bigO{\int_{\Kcal_C(k_n)^2} \ind{|x-x^\prime| \le k_n^{1 + \varepsilon}} \rho_{y}(k) 
		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y) f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy}\\
	&= \bigO{k_n^{1+\varepsilon} \binom{k_n}{2} \left(\int_{a_n^-}^{a_n^+} \Delta_{\Pcal}(y^\prime) 
			e^{-\alpha y^\prime} \, dy^\prime\right) \Exp{T_{\Pcal,n}(k_n)}}\\
	&= \bigO{k_n^{3 + \varepsilon -2\alpha} s_\alpha(k_n) \Exp{T_{\Pcal,n}(k_n)}}\\
	&= \smallO{n k_n^{-(2\alpha - 1)}s_\alpha(k_n) \Exp{T_{\Pcal,n}(k_n)}} = \smallO{\Exp{T_{\Pcal,n}(k_n)}^2},
\end{align*}
which proves \eqref{eq:I_ab_ast_main}. Here we used that $k_n^{2 + \varepsilon} = \smallO{n}$ and $\Exp{T_{\Pcal,n}(k_n)} = \bigT{n k_n^{-(2\alpha - 1)}s_\alpha(k_n)}$ for the last line.
